---
title: "TV Ratings"
output: github_document
always_allow_html: true
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tvrating

<!-- badges: start -->
<!-- badges: end -->

The goal of tvrating is to introduce the user to the package and aid them with using it.

## Installation

You can install the development version of `tvrating` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ETC5523-2023/rpkg-bilallovesbatman")
```

# Loading the Package

To be able to use the package and access the data, the user must load `tvrating` from the library and calling the object `tvrating`

```{r setup, include = FALSE}
library(plotly)
library(tidyverse)
library(tvrating)
```

# Use-case Examples

## Example 1: 5-Number Summary

This package contains functions that allows users to be able to process or manipulate the data. As an example, the user can use the `summary_tv` function to calculate the famous **five number summary** of the show ratings (column: `av_rating`) i.e. minimum, Q1, median, Q3, maximum. Returns NULL if inputs are less than a total of 5. 

```{r process}
summary_tvrating(tv_ratings)
```

## Example 2: Genre Distribution

Another example is being able to plot the genre distribution plot based on the selected top genres using the filter. The user must use the following command:

```{r}
genre_plot(tv_ratings, selected_genre = 5)
```

The distribution of different genres is plotted based on the user's selection on the filter.
