---
title: "TV Ratings"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tvrating}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

## Data Description

This dataset contains TV Shows from the years 1990 through till 2018 including their:

* Title ID: unique id for the show
* Season Number: Season number of the show
* Date of Release: Date when show was released
* Average Rating of Season: Average rating of a season of a show
* Share of Viewership: Average viewership share of a season of a show
* Genres: Genre of the show

The data is originally 
from **The Economist** [Data GitHub](https://github.com/TheEconomist) via IMDb from
1990 to 2018 and found on the `tidytuesday` repository of `rfordatascience` which can be found [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-01-08).

Some outstanding data analysis and visualizations were already conducted by the data experts from **The Economist** which can be found in their [article](https://www.economist.com/graphic-detail/2018/11/24/tvs-golden-age-is-real) which is why a decision was taken to conduct our own analysis journey and leaving this masterpiece alone.


# Loading the Package

To be able to use the package and access the data, the user must load `tvrating` from the library and calling the object `tvrating`

```{r setup, include = FALSE}
library(plotly)
library(tidyverse)
library(tvrating)
```

# Using the package:

## Example 1: 5-Number Summary

This package contains functions that allows users to be able to process or manipulate the data. As an example, the user can use the `summary_tv` function to calculate the famous **five number summary** of the show ratings (column: `av_rating`) i.e. minimum, Q1, median, Q3, maximum. Returns NULL if inputs are less than a total of 5. 

```{r process}
summary_tvrating(tv_ratings)
```

## Example 2: Genre Distribution

Another example is being able to plot the genre distribution plot based on the selected top genres using the filter. The user must use the following command:

```{r}
genre_plot(tv_ratings, selected_genre = 5)

```

The distribution of different genres is plotted based on the user's selection on the filter.

# That's All!

These are the basics a user needs to get along with the 2 essential functions provided in the `tvrating` package. These functions are a great starting point to analyze the TV ratings data. For more details, please refer to the package documentation.
